---
title: "Visualization of survey Risk perception of COVID-19/coronavirus"
author: "UnEviL Research Group, Lund University"
date: "12/04/2020"
output: 
  html_document: 
    code_folding: hide
    theme: paper
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
lang <- "en"
knitr::opts_chunk$set(echo=FALSE, message=FALSE, error=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(comment=FALSE))
knitr::read_chunk('survey_chunks.R')
```

## Introduction

This document visualizes results of the international [survey by Winton Centre for Risk and Evidence Communication](https://www.cam.ac.uk/stories/wintoncovid1) about people's attitudes towards the risk of coronavirus, and their governments’ reactions.

```{r prepare_data}

```


```{r service_functions}

```

## Trust

```{r trust_1, fig.width=7, fig.height=4}

```


```{r trust_2, fig.width=12, fig.height=24}

```

## COVID-19 Experience

```{r covid_1, fig.width=12, fig.height=12}

```

```{r covid_2, fig.width=12, fig.height=8}

```

```{r sars_1, fig.width=7, fig.height=4}

```

## Cultural perception

```{r cultcog_1, fig.width=12, fig.height=12}

```

```{r prosocial_1, fig.width=7, fig.height=4}

```

## Personal attitudes

```{r canadaq_1, fig.width=12, fig.height=9}

```

```{r finitepool_1, fig.width=12, fig.height=16}

```

```{r longitude_1, fig.width=12, fig.height=8}

```

```{r personal_1, fig.width=12, fig.height=16}

```

```{r friends_1, fig.width=12, fig.height=16}

```

## Media exposure and trust

```{r mediaexp_1, fig.width=12, fig.height=16}

```

```{r mediaexp_2, fig.width=12, fig.height=16}

```

## Personal investigation and actions

```{r soughtinfo_1, fig.width=7, fig.height=4}

```

```{r prep_1,  fig.width=7, fig.height=4}

```

## Government response

```{r govresponse_1, fig.width=12, fig.height=18}

```

```{r govresponse_2, fig.width=12, fig.height=8}

```

## Science understanding

```{r sciunderstand_1, fig.width=7, fig.height=4}

```

```{r sciunderstand_2, fig.width=12, fig.height=5}

```

```{r sciunderstand_3, fig.width=12, fig.height=5}

```
