---
title: "Risk perception of COVID-19/coronavirus"
author: "[Uncertainty and Evidence Lab](https://www.cec.lu.se/research/unevil)  \nLund University"
date: "14/04/2020"
output: 
  html_document: 
    theme: paper
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}
lang <- "en"
knitr::opts_chunk$set(echo=FALSE, message=FALSE, error=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(comment=FALSE))
knitr::read_chunk('survey_chunks.R')
```

## Introduction

This document visualizes results of the international [survey by Winton Centre for Risk and Evidence Communication](https://www.cam.ac.uk/stories/wintoncovid1) about people's attitudes towards the risk of coronavirus, and their governments’ reactions.
Data were collected in the period 19 - 29th of March 2020. 
```{r prepare_data}

```


```{r service_functions}

```

## Trust

```{r trust_1, fig.width=7, fig.height=5}

```


```{r trust_2, fig.width=12, fig.height=28}

```

## Experience of COVID-19

```{r covid_1, fig.width=12, fig.height=14}

```

## Effects from COVID-19

```{r covid_2, fig.width=12, fig.height=9}

```

## Experiences of similar diseases

```{r sars_1, fig.width=7, fig.height=5}

```

## Cultural perception

```{r cultcog_1, fig.width=12, fig.height=14}

```

```{r prosocial_1, fig.width=7, fig.height=5}

```

## Risk perception of COVID-19

```{r canadaq_1, fig.width=12, fig.height=10}

```

## Worry of COVID-19

```{r finitepool_1, fig.width=12, fig.height=18}

```

```{r longitude_1, fig.width=12, fig.height=9}

```

## Direct and personal effects

```{r personal_1, fig.width=12, fig.height=18}

```

## Direct effects on friends and family

```{r friends_1, fig.width=12, fig.height=18}

```

## Use and trust in information

```{r mediaexp_1, fig.width=12, fig.height=18}

```

```{r mediaexp_2, fig.width=12, fig.height=18}

```

## Preparedness

```{r soughtinfo_1, fig.width=7, fig.height=4}

```

```{r prep_1,  fig.width=7, fig.height=5}

```

## Governmental response

```{r govresponse_1, fig.width=12, fig.height=20}

```

```{r govresponse_2, fig.width=12, fig.height=9}

```

## Scientific knowledge

```{r sciunderstand_1, fig.width=7, fig.height=5}

```

```{r sciunderstand_2, fig.width=12, fig.height=5}

```

## Vaccine

```{r vaccine_1, fig.width=12, fig.height=5}

```
