---
title: "Risk perception of COVID-19/coronavirus"
author: "[Uncertainty and Evidence Lab](https://www.cec.lu.se/research/unevil)  \nLund University"
date: "14/04/2020"
output: 
  html_document: 
    theme: paper
    toc: yes
    toc_float: yes
bibliography: bibliography.bib
---

```{r setup, include=FALSE}
lang <- "en"
knitr::opts_chunk$set(echo=FALSE, message=FALSE, error=FALSE, warning=FALSE, tidy=TRUE, tidy.opts=list(comment=FALSE))
knitr::read_chunk('survey_chunks.R')
```

## Introduction

This document visualizes results of the international [survey by Winton Centre for Risk and Evidence Communication](https://www.cam.ac.uk/stories/wintoncovid1) about people's attitudes towards the risk of coronavirus, and their governments’ reactions. For details see article [published in the Journal of Risk Research on 05 May 2020](https://doi.org/10.1080/13669877.2020.1758193) [@dryhurst2020].

Data were collected during March and April 2020. 

```{r prepare_data}

```


```{r service_functions}

```

## Percieved effects from COVID-19

```{r covid_2, fig.width=12, fig.height=9}

```

## Percieved risk of COVID-19 

```{r canadaq_1, fig.width=12, fig.height=10}

```

## Worry about COVID-19

```{r longitude_1, fig.width=12, fig.height=9}

```

## Worry about COVID-19 compared to other issues

```{r finitepool_1, fig.width=12, fig.height=18}

```

## Risk perception of COVID-19 compared to other issues - direct and personal effects

```{r personal_1, fig.width=12, fig.height=18}

```

## Risk perception of COVID-19 compared to other issues - effects on friends and family

```{r friends_1, fig.width=12, fig.height=18}

```

## View on vaccination for COVID-19

```{r vaccine_1, fig.width=12, fig.height=5}

```

## Information about COVID-19

```{r soughtinfo_1, fig.width=7, fig.height=4}

```

```{r mediaexp_1, fig.width=12, fig.height=18}

```

## Trust in information about COVID-19
```{r mediaexp_2, fig.width=12, fig.height=18}

```

## View on scientific knowledge about COVID-19

```{r sciunderstand_1, fig.width=7, fig.height=5}

```

```{r sciunderstand_2, fig.width=12, fig.height=5}

```

## View on govermental responses

```{r govresponse_1, fig.width=12, fig.height=20}

```

```{r govresponse_2, fig.width=12, fig.height=9}

```

## Trust in individuals and society

```{r trust_1, fig.width=7, fig.height=5}

```

```{r trust_2, fig.width=12, fig.height=28}

```

## View on individuals and society

```{r cultcog_1, fig.width=12, fig.height=14}

```

```{r prosocial_1, fig.width=7, fig.height=5}

```

## Experiences of COVID-19 or similar diseases

```{r covid_1, fig.width=12, fig.height=14}

```

```{r sars_1, fig.width=7, fig.height=5}

```

```{r prep_1,  fig.width=7, fig.height=5}

```

## Risk perception index 

As shown in [@dryhurst2020], risk perception can be aggregated into an index, which combines answers to the following questions

```{r idx_var_1}

```
<br>
Rescaling of questions on 1..5 scale is done with $NewScore = OldScore * 1.5 - 0.5$. One of the question is stated with negation (i.e. "will NOT affect"), so the answers need to be inverted. Once the scores are rescaled they can be averaged across the answers to the questions in the table above. 

Now we can compare distribution of Risk index by country.

```{r idx_var_2, fig.width=7, fig.height=6}

```


## References
